### 2024-02-18 sections/4gluing.tex
Add files via upload

    Checking (2) amounts to evaluating disks $U$ which are contained in only one of the pieces $M_-$, $M_0 \times \mathbb{R}$ and $M_+$. For the case of $U_0 \times \mathbb{R} = \emptyset = U_+$, we have
    %
    \begin{equation}
        A(U) = \int_{U} A_- \bigotimes\limits_{\mathbb{1}} \mathbb{1} \simeq A_- (U),
    \end{equation}
    %
    and similarly if $U_- = \emptyset = U_0 \times \mathbb{R}$. Alternatively, for the case of $U_- = U_0 \times \mathbb{R} = U_+$ we instead have
    %
    \begin{equation}
        A(U) = \int_U A_0 \bigotimes\limits_{\int_{U} A_0} \int_U A_0 \simeq A_0(U).
    \end{equation}
    %
    If $U$ is such that $U_+ = \emptyset$, but $U_0 \times \mathbb{R} \neq \emptyset$ then
    %
    \begin{equation}
        A(U) = \int_U A_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A_-} \mathbb{1} \simeq \int_U A_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A_-} \int_{\emptyset} A_- \simeq \int_{U} A_- = A_-(U),
    \end{equation}
    %
    where the last equivalence is provided by the collar-gluing property of factorization homology. This observation is also what confirms (3).

    Finally, we want to show that $\rho$ is fully faithful, i.e. we need to show that it is an equivalence of morphism spaces
    %
    \begin{equation}
        \mathsf{Hom}_{\alg{\disk_{/M}} (\catC)}(A, B) \simeq \mathsf{Hom}_{\mathscr{P}}((A_-, A_+), (B_-, B_+)),
    \end{equation}
    %
    for each $A, B \in \alg{\disk_{/M}} (\catC)$. By the definition of algebras over an $\infty$-operad we have that $\alg{\disk_{/M}} (\catC)$ is a full $\infty$-subcategory of $\mathsf{Fun}(\disk_{/M}, \catC)$, which reduces the problem to showing that
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{Hom}_{\mathsf{Fun}(\disk_{/M}, \catC)}(A, B) \arrow[r, bend left=4, "\rho"] & \mathsf{Hom}_{\mathscr{P}}((A_-, A_+), (B_-, B_+)) \arrow[l, bend left=4, "\gamma"]
        \end{tikzcd}
    \end{equation}
    %
    gives rise to an equivalence. Similar computations as in checking (2) and (3) above yield the necessary requirements.
\end{proof}

@@

\begin{corollary}\label{cor:gluing_lcfas}
    A collar-gluing of smooth manifolds $f: M \rightarrow [-1,1]$ induces an equivalence of $\infty$-categories
    %
    \begin{equation}
        \lcfa_M (\catC) \simeq \lcfa_{M_-} (\catC) \bigtimes_{\lcfa_{M_0 \times \mathbb{R}} (\catC)} \lcfa_{M_+}(\catC).
    \end{equation}
\end{corollary}

@@

\begin{example}\label{ex:reproduce_lcfas_on_S1}
    Using results from \cite[prop.4.0.1]{cg2016}, namely inheritance from a covering space, \cite[sec.5.5]{ginot2015} characterizes locally constant factorization algebras on the circle $S^1$ as
    %
    \begin{equation}
        \lcfa_{S^1} (\catC) \simeq \aut (\alg{\mathbb{E}_1} (\catC)),
    \end{equation}
    %
    as $\mathbb{E}_1$-algebras together with a self-equivalence. \Cref{cor:gluing_lcfas} allows us to recover this nontrivial result. To wit, the circle can be exhibited as a collar-gluing $S^1 \cong \mathbb{R} \coprod_{S^0 \times \mathbb{R}} \mathbb{R} \cong \mathbb{R} \coprod_{\mathbb{R} \sqcup \mathbb{R}} \mathbb{R}$. For locally constant factorization algebras this means that
    %
    \begin{equation}\label{eq:lcfas_on_S1_gluing}
        \lcfa_{S^1} (\catC) \simeq \lcfa_{\mathbb{R}} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \alg{\mathbb{E}_1} (\catC).
    \end{equation}
    %
    Since a disjoint union is a collar-gluing we also have that $\lcfa_{\mathbb{R} \sqcup \mathbb{R}} \simeq \lcfa_{\mathbb{R}} (\catC) \times \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \times \alg{\mathbb{E}_1} (\catC)$. Let's denote the restriction functors that restrict to the first and the second component of the disjoint union $\mathbb{R} \sqcup \mathbb{R}$ by $|_1$ and $|_2$ respectively. Going back to \cref{eq:lcfas_on_S1_gluing}, the data of a locally constant factorization algebra on $S^1$ is equivalent to the data of two $\mathbb{E}_1$-algebras $A$ and $B$ such that their restrictions $A|_1 = B|_1$ and $A|_2 = B|_2$ agree. Since all of these are $\mathbb{E}_1$-algebras there are equivalences with the restrictions forming
    %
    \begin{equation}
        \begin{tikzcd}[row sep = small, column sep= small]
            & A|_1 \arrow[r, phantom, "=", description] & B|_1 & \\
            A \arrow[rd, phantom, "\simeq", sloped, description] \arrow[ru, phantom, "\simeq", sloped, description] & & & B \arrow[lu, phantom, "\simeq", sloped, description] \arrow[ld,  phantom, "\simeq", sloped, description] \\
            & A|_2 \arrow[r, phantom, "=", description] & B|_2 &                        
        \end{tikzcd}
    \end{equation}
    %
    That is we have the data of two algebras $A$ and $B$, and two equivalences from $A$ to $B$. It is standard that this data is equivalent (in one direction by composing) to the data of an $\mathbb{E}_1$-algebra with a self-equivalence.
\end{example}

\begin{example}\label{ex:lcfas_on_S^n}
    Just as for the circle, higher spheres can also be described as a collar-gluing $S^n \cong \mathbb{R}^n \coprod_{S^{n-1} \times \mathbb{R}} \mathbb{R^n}$. Thus, we can iterate the procedure from \cref{ex:reproduce_lcfas_on_S1} to get the locally constant factorization algebras on all higher spheres. For example, for the two-sphere $S^2$ we have
    %
    \begin{equation}
        \lcfa_{\mathbb{R}^2}(\catC) \bigtimes_{\lcfa_{S^1 \times \mathbb{R}}(\catC)} \lcfa_{\mathbb{R}^2}(\catC) \simeq \alg{\mathbb{E}_2}(\catC) \bigtimes_{\alg{\mathbb{E}_1}( \aut (\alg{\mathbb{E}_1} (\catC))) } \alg{\mathbb{E}_2} (\catC),
    \end{equation}
    %
    namely, a locally constant factorization algebra on $S^2$ equivalent to two $\mathbb{E}_2$-algebras, such that they restrict on the fattened equator to the same $\mathbb{E}_2$-algebra equipped with an $\mathbb{E}_1$-automorphism. It is nontrivial to describe this data in a simpler way as was possible for $S^1$. We can see, though, that for the higher spheres there are higher coherent equivalences that locally constant factorization algebras keep track of.
\end{example}

>>>>

    Checking (2) amounts to evaluating disks $U$ which are contained in only one of the pieces $M_-$, $M_0 \times \mathbb{R}$ and $M_+$. For the case of $U_0 \times \mathbb{R} = \emptyset = U_+$, we have
    %
    \begin{equation}
        A(U) = \int_{U} A_- \bigotimes\limits_{\mathbb{1}} \mathbb{1} \simeq A_- (U),
    \end{equation}
    %
    and similarly if $U_- = \emptyset = U_0 \times \mathbb{R}$. Alternatively, for the case of $U_- = U_0 \times \mathbb{R} = U_+$ we instead have
    %
    \begin{equation}
        A(U) = \int_U A_0 \bigotimes\limits_{\int_{U} A_0} \int_U A_0 \simeq A_0(U).
    \end{equation}
    %
    If $U$ is such that $U_+ = \emptyset$, but $U_0 \times \mathbb{R} \neq \emptyset$ then
    %
    \begin{equation}
        A(U) = \int_U A_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A_-} \mathbb{1} \simeq \int_U A_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A_-} \int_{\emptyset} A_- \simeq \int_{U} A_- = A_-(U),
    \end{equation}
    %
    where the last equivalence is provided by the collar-gluing property of factorization homology. This observation is also what confirms (3). Namely,
    %
    \begin{equation}
        \int_U A \simeq \int_{U_-} A \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A} \int_{U_+} A \simeq \int_{U_-} A_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A_0} \int_{U_+} A_+,
    \end{equation}
    %
    where the first equivalence comes from collar-gluing, while the second is a rewriting using the fact that restricting the algebra doesn't change the value of factorization homology it just changes what we can evaluate with it.

    Finally, we want to show that $\rho$ is fully faithful, i.e. we need to show that it is an equivalence of morphism spaces
    %
    \begin{equation}
        \mathsf{Hom}_{\alg{\disk_{/M}} (\catC)}(A, B) \simeq \mathsf{Hom}_{\mathscr{P}}((A_-, A_+), (B_-, B_+)),
    \end{equation}
    %
    for each $A, B \in \alg{\disk_{/M}} (\catC)$. By the definition of algebras over an $\infty$-operad we have that $\alg{\disk_{/M}} (\catC)$ is a full $\infty$-subcategory of $\mathsf{Fun}(\disk_{/M}, \catC)$, and since we already expressed the construction functorially with $\rho$ and $\gamma$, all that remains to be checked is that the already defined maps
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{Hom}_{\mathsf{Fun}(\disk_{/M}, \catC)}(A, B) \arrow[r, bend left=4, "\rho"] & \mathsf{Hom}_{\mathscr{P}}((A_-, A_+), (B_-, B_+)) \arrow[l, bend left=4, "\gamma"]
        \end{tikzcd}
    \end{equation}
    %
    gives rise to an equivalence. That is, we have to do similar computations as (2) and (3) above, but now on the level of morphisms. Nothing new happens in the case of (2) since its logic essentially only depends on the properties of the bar construction when restricting. In the case of (3) we crucially used the collar-gluing property of factorization homology. That this property continues to hold at the morphism level is a consequence of the fact that \cref{prop:barconst=intinterval} is an equivalence not only at the level of objects, but also at the level of functors, together with the pushforward property which also holds functorially à la \cref{rem:fh_pushforward_functorial}.
\end{proof}

@@

\begin{corollary}\label{cor:gluing_lcfas}
    A collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$ induces an equivalence of $\infty$-categories
    %
    \begin{equation}
        \lcfa_M (\catC) \simeq \lcfa_{M_-} (\catC) \bigtimes_{\lcfa_{M_0 \times \mathbb{R}} (\catC)} \lcfa_{M_+}(\catC).
    \end{equation}
\end{corollary}

@@

\begin{example}\label{ex:reproduce_lcfas_on_S1}
    Using results from \cite[prop.4.0.1]{cg2016}, namely inheritance from a covering space, \cite[sec.5.5]{ginot2015} characterizes locally constant factorization algebras on the circle $S^1$ as
    %
    \begin{equation}
        \lcfa_{S^1} (\catC) \simeq \aut (\alg{\mathbb{E}_1} (\catC)),
    \end{equation}
    %
    i.e. $\mathbb{E}_1$-algebras together with a self-equivalence. \Cref{cor:gluing_lcfas} allows us to recover this nontrivial result. To wit, the circle can be exhibited as a collar-gluing $S^1 \cong \mathbb{R} \coprod_{S^0 \times \mathbb{R}} \mathbb{R} \cong \mathbb{R} \coprod_{\mathbb{R} \sqcup \mathbb{R}} \mathbb{R}$. For locally constant factorization algebras this means that
    %
    \begin{equation}\label{eq:lcfas_on_S1_gluing}
        \lcfa_{S^1} (\catC) \simeq \lcfa_{\mathbb{R}} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \alg{\mathbb{E}_1} (\catC).
    \end{equation}
    %
    Since a disjoint union is a collar-gluing we also have that $\lcfa_{\mathbb{R} \sqcup \mathbb{R}} \simeq \lcfa_{\mathbb{R}} (\catC) \times \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \times \alg{\mathbb{E}_1} (\catC)$. Let's denote the restriction functors that restrict to the first and the second component of the disjoint union $\mathbb{R} \sqcup \mathbb{R}$ by $|_1$ and $|_2$ respectively. Going back to \cref{eq:lcfas_on_S1_gluing}, the data of a locally constant factorization algebra on $S^1$ is equivalent to the data of two $\mathbb{E}_1$-algebras $A$ and $B$ such that their restrictions $A|_1 = B|_1$ and $A|_2 = B|_2$ agree. Since all of these are $\mathbb{E}_1$-algebras there are equivalences with the restrictions forming
    %
    \begin{equation}
        \begin{tikzcd}[row sep = small, column sep= small]
            & A|_1 \arrow[r, phantom, "=", description] & B|_1 & \\
            A \arrow[rd, phantom, "\simeq", sloped, description] \arrow[ru, phantom, "\simeq", sloped, description] & & & B \arrow[lu, phantom, "\simeq", sloped, description] \arrow[ld,  phantom, "\simeq", sloped, description] \\
            & A|_2 \arrow[r, phantom, "=", description] & B|_2 &                        
        \end{tikzcd}
    \end{equation}
    %
    That is we have the data of two algebras $A$ and $B$, and two equivalences from $A$ to $B$. It is standard that this data is equivalent (in one direction by composing) to the data of an $\mathbb{E}_1$-algebra with a self-equivalence.
\end{example}

\begin{example}\label{ex:lcfas_on_S^n}
    Just as for the circle, higher spheres can also be described as a collar-gluing $S^n \cong \mathbb{R}^n \coprod_{S^{n-1} \times \mathbb{R}} \mathbb{R^n}$. Thus, we can iterate the procedure from \cref{ex:reproduce_lcfas_on_S1} to get the locally constant factorization algebras on all higher spheres. For example, for the two-sphere $S^2$ we have
    %
    \begin{equation}
        \lcfa_{\mathbb{R}^2}(\catC) \bigtimes_{\lcfa_{S^1 \times \mathbb{R}}(\catC)} \lcfa_{\mathbb{R}^2}(\catC) \simeq \alg{\mathbb{E}_2}(\catC) \bigtimes_{\alg{\mathbb{E}_1}( \aut (\alg{\mathbb{E}_1} (\catC))) } \alg{\mathbb{E}_2} (\catC),
    \end{equation}
    %
    namely, a locally constant factorization algebra on $S^2$ is equivalent to two $\mathbb{E}_2$-algebras, such that they restrict on the fattened equator to the same $\mathbb{E}_2$-algebra equipped with an $\mathbb{E}_1$-automorphism. It is nontrivial to describe this data in a simpler way as was possible for $S^1$.

    From this example we can easily see that beyond the dimensionality $n$ of the space, which is locally kept track of as an $\mathbb{E}_n$-algebra, locally constant factorization algebras for the higher spheres also keep track of higher coherent (self-)equivalences.
\end{example}

### 2024-02-18 sections/5classification.tex
Add files via upload

Despite \cref{rem:disk_not_enough}, we know from \cref{lem:disk/M_to_disk} that sometimes the classification results for disk algebras can be used for factorization algebras. In particular, this is the case for $\mathbb{R}^{d \subset n}$, since it is final in the $\infty$-category of basics $\bstr = \mathsf{D}_{d \subset n}^*$. This gives us
%
\begin{equation}\label{eq:focus_on_disk_dn}
    \lcfa_{\mathbb{R}^{d \subset n}} (\catC) \simeq \alg{\disk (\mathsf{D}_{d \subset n}^*)} (\catC).
\end{equation}

In fact, technically, the only case we need to consider is when $d=0$. This is the case of pointed Euclidean spaces, which are alternatively denoted $\mathbb{R}^n_*$. This is because of the isomorphism
%
\begin{equation}
    \mathbb{R}^{d \subset n} \cong \mathbb{R}^{n-d}_* \times \mathbb{R}^d,
\end{equation}
%
together with \cref{prop:exp_of_products_lc}, which describes locally constant factorization algebras on product spaces. To get a better grasp on $\mathbb{R}^n_*$ case we examine the $\infty$-operad.

\begin{observation}
    For the purposes of the observation we will shorten notation to $\mathscr{D}_* := \disk (\mathsf{D}_{0 \subset n}^*)$. Since the defect is a point there can be at most one disk that contains it per morphism. Thus, the morphism spaces to consider are
    %
    \begin{align}
        &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n),& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*)& &\mathrm{and}& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*).&
    \end{align}
    %
    The first of these is equivalent to the space $\mathsf{Emb}^*((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n)$ of framed open embeddings, which makes it is obvious that restricting to non-defect disks would give the data of an $\mathbb{E}_n$-algebra. When $i=0$, the third space above is equivalent to a point, which makes it clear that restricting exclusively to pointed disks $\mathbb{R}^n_*$ we give rise to plain objects\footnote{We've omitted mentioning the fact that, because of morphisms like $\emptyset \xrightarrow{} U$, all of the above algebraic objects will be pointed. We have done this to avoid confusion with the use of pointed in the sense of a point defect of the space.} (or $\mathbb{E}_0$-algebra). The structure that connects the two algebras is encoded in the rest of the morphism spaces.

    By definition, the middle space is given by $\mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\})$. For the last space when $i$ isn't necessarily 0 we can use the same observation as in the proof of \cite[prop.3.16]{francis2013}, namely that we can always translate the disks so that the defect lands at the origin. This gives an equivalence of spaces
    %
    \begin{equation}
        \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*) \simeq \mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\})
    \end{equation}
    %
    to the framed embeddings that miss the origin. Comparing to the proof of \cref{univ_env_for_En} this suggests that
\end{observation}

\begin{theorem}
    Let $n$ be bigger than 1. There is an equivalence between the $\infty$-category of locally constant factorization algebras on $\mathbb{R}^n_*$ and the $\infty$-category of $\mathbb{E}_n$-modules
    %
    \begin{equation}
        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n_*} (\catC).
    \end{equation} 
\end{theorem}

@@

.....

The study of these was undertaken in \cite{ginot2015}. There it was shown that

\begin{theorem}[{\cite[cor.8]{ginot2015}}]\label{thm:ginot_classif_Rn*}
    Let $n$ be bigger than 1. There is an equivalence between the $\infty$-categories of $\mathbb{E}_n$-modules and the pullback
    %
    \begin{equation}
        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n_*} (\catC) \bigtimes_{\lcfa_{\mathbb{R}^n \setminus \{ 0\} } (\catC)} \lcfa_{\mathbb{R}^n} (\catC).
    \end{equation}
\end{theorem}

\begin{remark}
    The version of \cref{thm:ginot_classif_Rn*} cited above is different from the one appearing in the original reference. \cite[cor.8]{ginot2015}, as stated, requires the homotopy pullback, however examining its proof and the later \cite[cor.9]{ginot2015} implies that the correct statement that has been proven is as written above.
\end{remark}

\begin{remark}
    The case of $n=1$ is special because the higher stratum $\mathbb{R} \setminus \{0\}$ is now disconnected. Looking back at the construction leading up to \cref{prop:hoint_gives_modules} and at \cref{rem:left_or_right_module} we can guess that a statement like the following can hold true:
\end{remark}

\begin{proposition}
    There is an equivalence between the $\infty$-category of locally constant factorization algebras on $\mathbb{R}_*$ and the $\infty$-category consisting of two $\mathbb{E}_1$-algebras $A$ and $B$ together with a pointed, left $A \otimes B^\mathsf{op}$-module $M$
    %
    \begin{equation}
        \lcfa_{\mathbb{R}_*} \simeq \mathsf{LMod} (\catC) \bigtimes_{\catC^{\mathbb{1}/}} \mathsf{RMod} (\catC),
    \end{equation}
    %
    where the functors $\mathsf{LMod}(\catC) \rightarrow \catC^{\mathbb{1}/}$ and $\mathsf{RMod}(\catC) \rightarrow \catC^{\mathbb{1}/}$ are the ones giving the underlying (pointed) object of a module.
\end{proposition}

>>>>

Despite \cref{rem:disk_not_enough}, we know from \cref{lem:disk/M_to_disk} that sometimes the classification results for disk algebras can be used for factorization algebras. In particular, this is the case for $\mathbb{R}^{d \subset n}$, since it is final in the $\infty$-category of basics $\bstr = \mathsf{D}_{d \subset n}^*$, as long as $d < n - 1$. This gives us
%
\begin{equation}\label{eq:focus_on_disk_dn}
    \lcfa_{\mathbb{R}^{d \subset n}} (\catC) \simeq \alg{\disk (\mathsf{D}_{d \subset n}^*)} (\catC).
\end{equation}

In fact, technically, the only cases we need to consider are when $d=0$ --- the case of pointed Euclidean spaces, which are alternatively denoted $\mathbb{R}^n_*$. This is because of the isomorphism
%
\begin{equation}
    \mathbb{R}^{d \subset n} \cong \mathbb{R}^{n-d}_* \times \mathbb{R}^d,
\end{equation}
%
together with \cref{prop:exp_of_products_lc}, which describes locally constant factorization algebras on product spaces. Since $\mathbb{R}^n_*$ is a basic the collar-gluing property \cref{cor:gluing_lcfas} can't help us to analyze the situation. We are left with two cases: $n=1$ and $n > 1$. To get a better grasp on the data, we first explore the more complicated case of $n > 1$ by examining the $\infty$-operad $\disk(\mathsf{D}_{0 \subset n}^*)$, when $n > 1$.

\begin{observation}
    For the purposes of the observation we will shorten notation to $\mathscr{D}_* := \disk (\mathsf{D}_{0 \subset n}^*)$. Since the defect is a point there can be at most one disk that contains it per morphism. Thus, the morphism spaces to consider are
    %
    \begin{align}
        &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n),& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*)& &\mathrm{and}& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*).&
    \end{align}
    %
    The first of these is equivalent to the space $\mathsf{Emb}^*((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n)$ of framed open embeddings, which makes it is obvious that restricting to non-defect disks would give the data of an $\mathbb{E}_n$-algebra. This is related to \cref{lem:ff_functor_to_refinement}, which says that forgetting the stratification results in obtaining a full $\infty$-subcategory of locally constant factorization algebras. When $i=0$, the third space above is equivalent to a point, which makes it clear that restricting exclusively to pointed disks $\mathbb{R}^n_*$ would give rise to plain objects\footnote{We've omitted mentioning the fact that, because of morphisms like $\emptyset \xrightarrow{} U$, all of the above algebraic objects will be pointed. We have done this to avoid confusion with the use of pointed in the sense of a point defect of the space.} (or $\mathbb{E}_0$-algebras).

    The structure that connects these two algebras is encoded in the rest of the morphism spaces. In fact the second and third space above are equivalent,
    %
    \begin{equation}
        \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*) \simeq \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*) \simeq \mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\}),
    \end{equation}
    %
    for all $i \in \mathbb{N}$, where $\mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\})$ is the space of framed embeddings of $i$ $n$-dimensional disks into the punctured $\mathbb{R}^n$.

    The isomorphism $\mathbb{R}^n \setminus \{ 0 \} \cong S^{n-1} \times \mathbb{R}$ together with an examination of \cite[prop.3.16]{francis2013}, which we recalled in \cref{univ_env_for_En}, and its proof leads us to suggest that the $\mathbb{E}_n$-algebra $A$ and the $\mathbb{E}_0$-algebra $B$ are further such that $B$ is a module over the universal enveloping algebra $U_A \simeq \int_{S^{n-1}} A$ as an $\mathbb{E}_1$-algebra. Remembering that we limited the whole discussion to the case when $n>1$, we propose:
\end{observation}

\begin{theorem}
    Let $n$ be bigger than 1. There is an equivalence between the $\infty$-category of locally constant factorization algebras on $\mathbb{R}^n_*$ and the $\infty$-category of $\mathbb{E}_n$-modules that fits into the commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{Mod}^{\mathbb{E}_n} (\catC) \arrow[r, "\simeq"] \arrow[d] & \lcfa_{\mathbb{R}^n_*} (\catC) \arrow[d, "\cref{lem:ff_functor_to_refinement}"] \\
            \alg{\mathbb{E}_n} (\catC) \arrow[r, "\simeq"] & \lcfa_{\mathbb{R}^n} (\catC).
        \end{tikzcd}
    \end{equation}
\end{theorem}

\begin{proof}
    Since $\mathsf{Mod}^{\mathbb{E}_n}$ is fibered over $\alg{\mathbb{E}_n}$, with fibers $\mathsf{Mod}^{\mathbb{E}_n}_A$ for $A$ an $\mathbb{E}_n$-algebra
\end{proof}

@@

%The study of these was undertaken in \cite{ginot2015}. There it was shown that

%\begin{theorem}[{\cite[cor.8]{ginot2015}}]\label{thm:ginot_classif_Rn*}
%    Let $n$ be bigger than 1. There is an equivalence between the $\infty$-categories of $\mathbb{E}_n$-modules and the pullback
%    %
%    \begin{equation}
%        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n_*} (\catC) \bigtimes_{\lcfa_{\mathbb{R}^n \setminus \{ 0\} } (\catC)} \lcfa_{\mathbb{R}^n} (\catC).
%    \end{equation}
%\end{theorem}

%\begin{remark}
%    The version of \cref{thm:ginot_classif_Rn*} cited above is different from the one appearing in the original reference. \cite[cor.8]{ginot2015}, as stated, requires the homotopy pullback, however examining its proof and the later \cite[cor.9]{ginot2015} implies that the correct statement that has been proven is as written above.
%\end{remark}

\begin{remark}
    The case $n=1$ is special because the higher stratum $\mathbb{R} \setminus \{0\}$ is now disconnected. Looking back at the construction leading up to \cref{prop:hoint_gives_modules} and at \cref{rem:left_or_right_module} we can guess that a statement like the following can hold true:
\end{remark}

\begin{proposition}
    There is an equivalence between the $\infty$-category of locally constant factorization algebras on $\mathbb{R}_*$ and the $\infty$-category consisting of two $\mathbb{E}_1$-algebras $A$ and $B$ together with a pointed, left $A \otimes B^\mathsf{op}$-module $M$
    %
    \begin{equation}
        \lcfa_{\mathbb{R}_*} \simeq \mathsf{LMod} (\catC) \bigtimes_{\catC_{\mathbb{1}/}} \mathsf{RMod} (\catC),
    \end{equation}
    %
    where the functors $\mathsf{LMod}(\catC) \rightarrow \catC_{\mathbb{1}/}$ and $\mathsf{RMod}(\catC) \rightarrow \catC_{\mathbb{1}/}$ are the ones giving the underlying (pointed) object of a module.
\end{proposition}
